Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2016-03-17 docs/questioning.tex
even better, with more original content

\titlespacing*{\section}
{0pt}{1ex}{0.8ex}
\titlespacing*{\subsection}
{0pt}{1ex}{0.8ex}
\titlespacing*{\subsubsection}
{0pt}{1ex}{0.8ex}

@@

% The rest of the paper is organized as follows:
% Section~\ref{sec:attacks} provides some insights on
% code injection attacks and
% Section~\ref{sec:model} presents our proposed model.
% Section~\ref{sec:dimensions} introduces the dimensions
% across which we analyze the various defenses.
% Our categorization and analysis is presented in
% Section~\ref{sec:defs} and a discussion is provided in
% Section~\ref{sec:discussion}. Finally,
% Section~\ref{sec:lessons-learned} highlights
% some lessons learned from our observations
% and Section~\ref{sec:conclusion} concludes the paper.

@@

Lack of input validation is a major vulnerability behind dangerous web
application attacks. By taking advantage of this, attackers can inject
their code into applications to perform malicious tasks. Exploits of
this kind can have different forms depending on the execution context
of the application and the location of the programming flaw that leads
to the attack~\cite{RL12b}.

% Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
% {\it ``unexpected (and unexpectedly powerful) computational models
%   inside targeted systems, which turn a part of the target into a
%   so-called `weird machine' programmable by the attacker via crafted
%   inputs (a.k.a. `exploits').''} In particular, {\it ``every
%   application that copies untrusted input verbatim into an output
%   program is vulnerable to code injection.''} Ray and
% Ligatti~\cite{RL12b} have proved this claim based on formal language
% theory.

@@

Detection mechanisms may impose a cost due to their use, as they
typically introduce some amount of extra computation on existing applications.
The overhead depends on the specifics of each mechanism. For
example, it may be due to some form of run-time checking, or some form of
obfuscation. Also, depending on the approach, the cost may be incurred
on different places: it may affect a server
(e.g., its memory or {\sc cpu} usage, processing throughput, or response latency),
it may affect the client, or both. The
usefulness of a mechanism depends therefore on the
computational cost it requires and on where it imposes it, as
different overheads may be acceptable at the server-side than the client-side.

What kind of numbers is reported matters as well. Reporting absolute
measurements gives little information on the actual overhead, unless
separate measurements are given for the system under study with and
without the proposed mechanism. Percentage measurements are normally
better.

@@

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.54]{defenses.pdf}
\end{center}
\vspace{-4.5mm}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application attacks based on code
injection. For each approach we provide the references
that present corresponding mechanisms:
{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
\vspace{-5mm}
\end{figure}

@@

    \multicolumn{5}{p{12.4cm}}{%
       $^\textsuperscript{1}$A check mark (\tick) indicates that the publication
       includes a link to a page where the software is available.
       {\bf AO} (Available On-line) indicates
       that the software is available on-line but the
       address is not mentioned in the paper, which probably means that
       the it was made available after the publication. A question 
       mark ({\bf ?}) indicates that a link to the software
       was included in the publication but is now inaccessible.
} \\
    \end{tabular}}
    \end{small}
    \end{threeparttable}
    \vspace{-5mm}
\end{table}

@@

For frameworks that deal with {\sc xss} attacks, we
see that attack detection and prevention may take place either at the server or
the client-side. In the first case, a proxy is typically placed in front of the server
to examine the server's responses before they reach a user's 
browser. In the second case, a modified browser or a library that is
securely downloaded from the server checks the responses for potential
attacks. We find that the tendency so far is to create frameworks that
perform detection on the client-side: in particular, 14 out of 24
frameworks (58,3\%) detect {\sc xss} attacks at the
client-side. Note that the majority of the mechanisms that detect
such attacks on the server can also detect {\sc dsl} code
injection attacks (6 out of 10).

>>>>

\titlespacing*{\section}
{0pt}{1ex}{0.6ex}
\titlespacing*{\subsection}
{0pt}{1ex}{0.6ex}
\titlespacing*{\subsubsection}
{0pt}{1ex}{0.6ex}

@@

The rest of the paper is organized as follows:
Section~\ref{sec:attacks} provides some insights on
web application attacks and
Section~\ref{sec:model} presents our proposed model.
Section~\ref{sec:dimensions} introduces the dimensions
across which we analyze the various defenses.
Our categorization and analysis is presented in
Section~\ref{sec:defs} and our observations are
provided in Section~\ref{sec:discussion}.
Finally, Section~\ref{sec:lessons-learned}
highlights some lessons learned from our observations
and Section~\ref{sec:conclusion} concludes the paper.

@@

Lack of input validation is a major vulnerability behind dangerous web
application attacks. By taking advantage of this, attackers can inject
their code into applications to perform malicious tasks. Exploits of
this kind can have different forms depending on the execution context
of the application and the location of the programming flaw that leads
to the attack.
Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
{\it ``unexpected (and unexpectedly powerful) computational models
  inside targeted systems, which turn a part of the target into a
  so-called `weird machine' programmable by the attacker via crafted
  inputs (a.k.a. `exploits').''} In particular, {\it ``every
  application that copies untrusted input verbatim into an output
  program is vulnerable to code injection.''} Ray and
Ligatti~\cite{RL12b} have proved this claim based on formal language
theory.

@@

Detection mechanisms may impose a cost due to their use, as they
typically introduce some amount of extra computation on existing applications.
The overhead depends on the specifics of each mechanism. For
example, it may be due to some form of run-time checking, or some form of
obfuscation. Also, depending on the approach, the cost may be incurred
on different places: it may affect a server
(e.g., its memory or {\sc cpu} usage, processing throughput, or response latency),
it may affect the client, or both. The
usefulness of a mechanism depends therefore on the
computational cost it requires and on where it imposes it, as
different overheads may be acceptable at the server-side than the client-side.
What kind of numbers is reported matters as well. Reporting absolute
measurements gives little information on the actual overhead, unless
separate measurements are given for the system under study with and
without the proposed mechanism. Percentage measurements are normally
better.

@@

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.54]{defenses.pdf}
\end{center}
\vspace{-5mm}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application attacks based on code
injection. For each approach we provide the references
that present corresponding mechanisms:
{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
\vspace{-6mm}
\end{figure}

@@

    \multicolumn{5}{p{12.4cm}}{%
       $^\textsuperscript{1}$A check mark (\tick) indicates that the publication
       includes a link to a page where the software is available.
       {\bf AO} (Available On-line) indicates
       that the software is available on-line but the
       address is not mentioned in the paper, which probably means that
       the it was made available after the publication. A question 
       mark ({\bf ?}) indicates that a link to the software
       was included in the publication but is now inaccessible.} \\
    \end{tabular}}
    \end{small}
    \end{threeparttable}
    \vspace{-7mm}
\end{table}

@@

For frameworks that deal with {\sc xss} attacks, we
see that attack prevention may take place either at the server or
the client-side. In the first case, a proxy is typically placed in front of the server
to examine the server's responses before they reach a user's 
browser. In the second case, a modified browser or a library that is
securely downloaded from the server checks the responses for potential
attacks. We find that the tendency so far is to create frameworks that
perform detection on the client-side: in particular, 14 out of 24
frameworks (58,3\%) detect {\sc xss} attacks at the
client-side. Note that the majority of the mechanisms that detect
such attacks on the server can also detect {\sc dsl} code
injection attacks (6 out of 10).
